### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Update 1_intro.tex

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. \cite{Alpher03}This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

@@

Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.\cite{Authors14b}

>>>>

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. \cite{Alpher03}This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies. \cite{Authors14b}

@@

Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.
